\documentclass[letterpaper, 11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames, dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

% --- packages for Icon --- %
\usepackage[dvipsnames]{xcolor}
\usepackage{tikz}
\usepackage{fontawesome5}

\pagestyle{fancy}

% -- clear all header and footer fields -- %
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% -- Adjust margins -- %
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% -- Sections formatting -- %
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% -- Ensure that generate pdf is machine readable/ATS parsable -- %
\pdfgentounicode=1

%% ----- Custom Commands Start ----- %%
\newcommand{\Item}[2]{\item\small{\textbf{#1}{#2 \vspace{-2pt}}}}
\newcommand{\SubItem}[2]{\Item{#1}{#2}\vspace{-4pt}}

\newcommand{\cItem}[2]{\item\small{\textbf{#1}{\textit{#2} \vspace{-2pt}}}}
\renewcommand{\labelitemii}{$\circ$}

\newcommand{\SubSecListBeg}{\begin{itemize}[leftmargin=*]}
\newcommand{\SubSecListEnd}{\end{itemize}}

\newcommand{\ItemListBeg}{\begin{itemize}}
\newcommand{\ItemListEnd}{\end{itemize}\vspace{-5pt}}

\newcommand{\subsecfourtwoitalic}[4] {
	\vspace{-1pt}\item
	\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{\small#3} & \textit{\small #4} \\
	\end{tabular*}\vspace{-5pt}
}

\newcommand{\subsubsectwoitalic}[2] {
	\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
		\textit{\small#1} & \textit{\small #2} \\
	\end{tabular*}\vspace{-5pt}
}

\newcommand{\subsectwonormal}[2] {
	\vspace{-1pt}\item
	\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
	\end{tabular*}\vspace{-5pt}
}

\newcommand{\subsectwooneitalic}[2] {
	\vspace{-1pt}\item
	\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
		\textbf{#1} & \textit{\small #2} \\
	\end{tabular*}\vspace{-5pt}
}

\newcommand{\linktable}[4] {
	\begin{tabular}{lr}
	#1 #2 \\
	#3 #4 \\
	\end{tabular}
}

%% ----- Custome Commands End ----- %%

% ---- CV SECTIONS ---- %
\begin{document}


% ---- HEADING ---- %
\textbf{\Huge Abd El-Twab M. Fakhry} \\

\begin{minipage}[t]{0.10\textwidth}
	\linktable
	{\faIcon{location-arrow}} {Cairo, Egypt}
	{\faIcon{mobile-alt}}     {(+20) 1127030951}
\end{minipage}
\hfill
\begin{minipage}[t]{0.20\textwidth}
	\linktable
	{\faIcon{envelope}} {abdeltwab.m.fakhry@protonmail.com}
	{\faIcon{linkedin}} {\href{https://www.linkedin.com/in/abdeltwabmf/}{linkedin.com/in/abdeltwabmf}}
\end{minipage}
\hfill
\begin{minipage}[t]{0.35\textwidth}
	\linktable
	{\faIcon{github}} {\href{https://github.com/AbdeltwabMF}{github.com/abdeltwabmf}}
	{\faIcon{code}}   {\href{https://codeforces.com/profile/Abd-Et-Twab}{codeforces.com/profile/abd-et-twab}}
\end{minipage}


% ---- EDUCATION ---- %
\section{Education}
\SubSecListBeg
	\subsecfourtwoitalic
	{\faIcon{university} Faculty of Engineering, Al-Azhar University} {Cairo, Egypt}
	{Bachelor in Computer Engineering}                                {Sep. 2017 -- Jun. 2022}
\SubSecListEnd

% ---- Competitive Programming ---- %
\section{Programming Contests Activity}
\SubSecListBeg
	\subsectwonormal
	{The Africa \& Arab Collegiate Programming Championship}{Luxor, Egypt}
	\ItemListBeg
		\cItem
		{2020}{: Ranked $98^{th}$}
	\ItemListEnd
	\subsectwonormal
	{The Egyptian Collegiate Programming Contest}{Alexandria, Egypt}
	\ItemListBeg
		\cItem
		{2020}{: Ranked $45^{th}$}
		\cItem
		{2019}{: Ranked $116^{th}$}
	\ItemListEnd
	\subsectwonormal
	{The Al-Azhar University Collegiate Programming Contest}{Cairo, Egypt}
	\ItemListBeg
		\cItem
		{2020}{: Ranked $2^{nd}$}
		\cItem
		{2019}{: Ranked $3^{rd}$}
	\ItemListEnd
	\subsectwonormal
	{IEEEXtreme Competition}{Online}
	\ItemListBeg
		\cItem
		{2020}{: Ranked $4^{th}$ on Egypt}
		\cItem
		{2019}{: Ranked $4^{th}$ on Egypt}
	\ItemListEnd
\SubSecListEnd


% ---- Experience and Volunteering ---- %
\section{Experience \& Volunteering}
\SubSecListBeg
	\subsecfourtwoitalic
	{Al-Azhar ICPC Community}{Cairo, Egypt}
	{Mentor and Problem-setter}{Feb. 2020 - Present}
      	\ItemListBeg
        	\Item{Writing Problems}
        	{: writing certain number of problems for weekly sheets and contests.}
		\Item{Training}
		{: Providing Multi-Level Training during the year; Teaching the participants Algorithms topics and Data Structures such as sorting, searching, graph theory and dynamic programming, Supporting Participants technically during sessions and online.}
      	\ItemListEnd
	\subsubsectwoitalic
	{Logistician}{Feb. 2020 - Present}
	\ItemListBeg
        	\Item{Events}
        	{: Managing and Booking every event.}
        	\Item{Training}
          	{: Providing and assure that all tools needed in training sessions are available (e.g. projector, white-board markers, etc…), as well as Providing yearly printed IDs and T-Shirts for all team members.}
      	\ItemListEnd
\SubSecListEnd


% ---- PROJECTS ---- %
\section{Projects}
\SubSecListBeg
	\subsectwooneitalic
	{\faIcon{user-clock} \href{https://github.com/AbdeltwabMF/Queueing-ModelSim}{Queueing ModelSim}}{Dec. 2020}
	\ItemListBeg
		\Item{}{Implemented a software for the calculation of characteristics of different queues having the BMAP (batch Markovian Arrival Process) as a input, as well as the deterministic queues.}
		\Item{Tools}
		{: Python3, Tkinter(GUI Programming), matplotlib.}
	\ItemListEnd

	\subsectwooneitalic
	{\faIcon{laptop-code} \href{https://github.com/AbdeltwabMF/Anthology-of-Algorithms-and-Data-structures}{Anthology of Algorithms and Data structures}}{Aug. 2020 -- Present}
	\ItemListBeg
		\Item{}{Implemented an open source library for Common Code for Competitive Programming in C++ including Graph Theory, Dynamic Programming, Mathematics, Computational Geometry, String Processing, Data Structures and more advanced topics, which i've learned through my training.}
		\Item{Tools}
		{: C++}
	\ItemListEnd
\SubSecListEnd

% ---- PROGRAMMING SKILLS ---- %
\section{Programming Skills}
\SubSecListBeg
	\Item{Programming Languages}{: C/C++, Python, Java, Matlab/GNU Octave, SQL, Bash/Shell, Emacs Lisp.}
	\Item{Markup Languages}{: \LaTeX, Markdown, HTML, CSS.}
	\Item{Technologies \& Tools}{: Linux, Git, GNU Debugger (gdb), Emacs, Docker.}
\SubSecListEnd


\end{document}
