\documentclass[letterpaper, 11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

% --- packages for Icon --- %
\usepackage[dvipsnames]{xcolor}
\usepackage{tikz}
\usepackage{fontawesome5}

\pagestyle{fancy}

% -- clear all header and footer fields -- %
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% -- Adjust margins -- %
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom\raggedright\setlength{\tabcolsep}{0in}

% -- Sections formatting -- %
\titleformat{\section}{\vspace{-4pt}\scshape\raggedright\large}{}{0em}{}[\color{black}\titlerule\vspace{-5pt}]

% -- Ensure that generate pdf is machine readable/ATS parsable -- %
\pdfgentounicode=1

%% ----- Custom Commands Start ----- %%
\newcommand{\education}[5] {
  \vspace{-1pt}\item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    #1 \textbf{#2} & #3 \\
    \textit{\small #4} & \textit{\small #5} \\
  \end{tabular*}
  \vspace{-4pt}
}

\newcommand{\extracurricularactivity}[5] {
\item\small
  {#1}
  \href{#2}{\color{RoyalBlue}#3}
  \href{#4}{\color{RoyalBlue}#5}
  \vspace{-4pt}
}

\newcommand{\experience}[7] {
  \vspace{-1pt}\item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    #1 \textbf{#2} \href{#4}{\color{RoyalBlue}#5} & #3 \\
    \textit{\small #6} & \textit{\small #7} \\
  \end{tabular*}
  \vspace{-8pt}
}

\newcommand{\subexperience}[1] {
\item\small
  {#1}
  \vspace{-2pt}
}

\newcommand{\project}[7] {
  \vspace{-1pt}\item
  \begin{tabular*}{0.97\textwidth}[t]{ll@{\extracolsep{\fill}}r}
    #1 \href{#4}{\textbf{\color{RoyalBlue}#2}} \textbar{} #7 \textbar{ } & \textit{#5} & \textit{\small #3} \\
    \vspace{-10pt}
  \end{tabular*}
  \textit{\small #6}
  \vspace{-8pt}
}

\newcommand{\subproject}[1] {
\item\small
  {#1}
  \vspace{-2pt}
}

\newcommand{\technicalskill}[3] {
  \vspace{-1pt}
\item\small
  #1 \textbf{#2 : }{\footnotesize{#3}}
  \vspace{-2pt}
}

\newcommand{\name}[2] {
  \textbf{
    \href{#1}{\Huge{#2}}
  }
  \vspace{-8pt}
}

\newcommand{\contact}[4] {
  \begin{tabular}{lr}
    {\href{#1}{\color{#3} #2 #4}}
  \end{tabular}
  \vspace{-4pt}
}

\newcommand{\bulletitem}[1] {{\tiny$\bullet$} #1}

\renewcommand{\labelitemii}{$\circ$}
%% ----- Custome Commands End ----- %%

% ---- CV SECTIONS ---- %
\begin{document}

% ---- HEADING ---- %
\name{http://abdeltwabmf.me}{Abd El-Twab M. Fakhry}

\begin{center}
  \small
  \contact
  {https://abdeltwabmf.github.io}
  {\faIcon{globe}}{RoyalBlue}{abdeltwabmf.me}\,
  \contact
  {https://www.linkedin.com/in/abdeltwabmf}
  {\faIcon{linkedin}}{RoyalBlue}{abdeltwabmf}\,
  \contact
  {https://github.com/AbdeltwabMF}
  {\faIcon{github}}{RoyalBlue}{abdeltwabmf}\,
  \contact
  {mailto:abdeltwab.m.fakhry@gmail.com}
  {\faIcon{envelope}}{RoyalBlue}{abdeltwab.m.fakhry@gmail.com}\,
  \contact
  {tel:+201127030951}
  {\faIcon{mobile-alt}}{RoyalBlue}{(+20) 1127030951}
\end{center}\vspace{8pt}

% ---- Education ---- %
\section{Education}
\begin{itemize}[leftmargin=*]
  \education
  {\faIcon{university}}
  {Faculty of Engineering, Al-Azhar University}{ Cairo, Egypt}
  {Bachelor in Computers and Systems Engineering}{ Sep. 2017 $-$ Jun. 2022}
\end{itemize}

% ---- Competitive Programming ---- %
\section{Extra-curricular Activities}
\begin{itemize}[leftmargin=*]
  \extracurricularactivity
  {Finalist at Africa \& Arab Collegiate Programming Championship (2020).}
  {https://icpc.global/ICPCID/S6R4YNB7PW7D}{\faIcon{link}}
  {https://drive.google.com/drive/folders/1u0_mdcJPAfc0o91xwnp9Y6JB8VDaY82e?usp=sharing}{\faIcon{link}}

  \extracurricularactivity
  {2x Finalist at Egyption Collegiate Programming Contest (2019, 2020).}
  {https://icpc.global/ICPCID/S6R4YNB7PW7D}{\faIcon{link}}
  {https://drive.google.com/drive/folders/1sjyZmHKeBmR2DB61ZGpJkiW17wtIWQ4q?usp=sharing}{\faIcon{link}}

  \extracurricularactivity
  {3rd \& 2nd palce at Al-Azhar Collegiate Programming Contest (2019, 2020).}
  {https://icpc.global/ICPCID/S6R4YNB7PW7D}{\faIcon{link}}
  {https://drive.google.com/drive/folders/18H79Bq42ARKxvx-H1pANSZgdD57EJMYF?usp=sharing}{\faIcon{link}}

  \extracurricularactivity
  {Teaching algorithmic topics, data structures, and problem-solving paradigms to +50 participants.}
  {https://sites.google.com/view/azharicpc/home}{\faIcon{link}}
  {}{}

  \extracurricularactivity
  {Providing multi-level training during the year and writing problems for weekly sheets and contests.}
  {https://sites.google.com/view/azharicpc/home}{\faIcon{link}}
  {}{}

  \extracurricularactivity
  {Solved +1000 algorithmic challenges on different online judges.}
  {https://github.com/AbdeltwabMF/online-judge-submissions-parser}{\faIcon{link}}
  {}{}
\end{itemize}

% ---- Experience and Volunteering ---- %
% \section{Experience \& Volunteering}
% \begin{itemize}[leftmargin=*]
%   \experience
%   {\faIcon{code}}
%   {Al-Azhar ICPC Community}{Cairo, Egypt}
%   {https://sites.google.com/view/azharicpc/home}{{\faIcon{link}}}
%   {Mentor and Problem-setter}{Feb. 2020 $-$ Present}

%   \begin{itemize}
%     \subexperience
%     {Providing multi-level training during the year and writing problems for weekly sheets and contests.}
%     \subexperience
%     {Teaching algorithmic topics, data structures, and problem-solving paradigms to +50 participants.}
%   \end{itemize}\vspace{-4pt}
% \end{itemize}

% ---- PROJECTS ---- %
\section{Selected Projects}
\begin{itemize}[leftmargin=*]
  \project
  {\faIcon{cloud}}
  {Decentralized Vault}{Jun. 2022 $-$ Present}
  {https://devault.vercel.app/}{Next.js - Hardhat - Ethers.js - Docker}
  {Blockchain-based, self-hosted, decentralized, and encrypted cloud storage system.}{2}

  \begin{itemize}
    \subproject
    {Developing a single-page application (SPA) using Next.js for static-site rendering (SSR).}
    \subproject
    {Implementing upgrade-able smart contracts for storing users' files metadata using the proxy pattern.}
    \subproject
    {Storing users' files after being encrypted using the IPFS p2p network.}
    \subproject
    {Using client-side encryption/decryption method for more confidentiality and privacy.}
  \end{itemize}\vspace{-4pt}

  \project
  {\faIcon{mosque}}
  {Next Prayer}{Sep. 2021 $-$ Present}
  {https://github.com/AbdeltwabMF/nxprayer}{C++ - Python - Docker}
  {Islamic prayer reminder for Unix status bars.}{Individual}

  \begin{itemize}
    \subproject
    {Implementing an Islamic prayer reminder for Unix status bars using web API.}
    \subproject
    {Maintaining an AUR (Arch-user repository) package and a Docker image for non-Unix users.}
  \end{itemize}\vspace{-4pt}

  \project
  {\faIcon{laptop-code}}
  {Anthology of Algorithms and Data structures}{Aug. 2020 $-$ Present}
  {https://github.com/AbdeltwabMF/Anthology-of-Algorithms-and-Data-structures}{C++}
  {Common code for competitive programming in C++.}{Individual}

  \begin{itemize}
    \subproject
    {Implementing an open-source library for common code for competitive programming in C++.}
    \subproject
    {Including graph theory, problem-solving paradigms, mathematics, and data structures.}
  \end{itemize}\vspace{-4pt}

  \project
  {\faIcon{user-clock}}
  {Queueing ModelSim}{Dec. 2020}
  {https://github.com/AbdeltwabMF/Queueing-ModelSim}{Python - Tkinter}
  {Queueing models simulator.}{Individual}

  \begin{itemize}
    \subproject
    {Implemented software that calculates the characteristics of queues with the markovian arrival process (MAP).}
    \subproject
    {Implemented a deterministic queue model using the prefix sum to easily identify the characteristics at any time.}
  \end{itemize}\vspace{-4pt}
\end{itemize}

% ---- Technical Skills ---- %
\section{Technical Skills}
\begin{itemize}[leftmargin=*]
  \technicalskill
  {\faIcon{code}}{Programming Languages}
  {C/C++ \bulletitem{Java} \bulletitem{Python} \bulletitem{Solidity} \bulletitem{JavaScript} \bulletitem{Bash/Shell} \bulletitem{SQL} \bulletitem{\LaTeX{}} \bulletitem{HTML/CSS}}

  \technicalskill
  {\faIcon{react}}{Technologies}
  {Next.js \bulletitem{Node.js} \bulletitem{PostgreSQL} \bulletitem{Hardhat} \bulletitem{Ethers.js}}

  \technicalskill
  {\faIcon{tools}}{Tools}
  {GNU/Linux \bulletitem{Git} \bulletitem{Make} \bulletitem{Emacs} \bulletitem{Vim} \bulletitem{Docker} \bulletitem{Jenkins} \bulletitem{Agile/Scrum} \bulletitem{Element}}
\end{itemize}

\end{document}
